Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-07-26 talk/vmil2012/paper.tex
Add a table showing the relative numbers of all operation types to explain the motivation

Although there are several publications about tracing just-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\todo{more motivation}
\todo{extend}
\todo{contributions, description of PyPy's guard architecture, analysis on benchmarks}
\begin{itemize}
 \item
\end{itemize}

@@

Figure~\ref{fig:ops_count} shows the total number of operations that are
recorded during tracing for each of the benchmarks on what percentage of these
are guards. Figure~\ref{fig:ops_count} also shows the number of operations left
after performing the different trace optimizations done by the trace optimizer,
such as xxx. The last columns show the overall optimization rate and the
optimization rate specific for guard operations, showing what percentage of the
operations was removed during the optimizations phase.

\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:ops_count}
\end{figure*}

\todo{resume data size estimates on 64bit}
\todo{figure about failure counts of guards (histogram?)}
\todo{integrate high level resume data size into Figure \ref{fig:backend_data}}
\todo{count number of guards with bridges for \ref{fig:ops_count}}
\todo{add resume data sizes without sharing}

@@

\todo{look into tracing papers for information about guards and deoptimization}
LuaJIT \todo{link to mailing list discussion}

>>>>

\begin{figure*}
    \include{figures/ops_count_table}
    \caption{Relative numbers of operations in the traces generated for
    different benchmarks}
    \label{fig:ops_count}
\end{figure*}
Although there are several publications about tracing just-in-time compilers, to
our knowledge, there are none that describe the use and implementation of
guards in this context. With the following contributions we aim to shed some
light (to much?) on this topic.
The contributions of this paper are:
\todo{more motivation}
\todo{extend}
\todo{contributions, description of PyPy's guard architecture, analysis on benchmarks}
\begin{itemize}
 \item
\end{itemize}

@@

Figure~\ref{fig:benchmarks} shows the total number of operations that are
recorded during tracing for each of the benchmarks on what percentage of these
are guards. Figure~\ref{fig:benchmarks} also shows the number of operations left
after performing the different trace optimizations done by the trace optimizer,
such as xxx. The last columns show the overall optimization rate and the
optimization rate specific for guard operations, showing what percentage of the
operations was removed during the optimizations phase.

\begin{figure*}
    \include{figures/benchmarks_table}
    \caption{Benchmark Results}
    \label{fig:benchmarks}
\end{figure*}

\todo{resume data size estimates on 64bit}
\todo{figure about failure counts of guards (histogram?)}
\todo{integrate high level resume data size into Figure \ref{fig:backend_data}}
\todo{add resume data sizes without sharing}
\todo{add a footnote about why guards have a threshold of 100}

@@

\todo{look into tracing papers for information about guards and deoptimization}
LuaJIT \todo{link to mailing list discussion}
http://lua-users.org/lists/lua-l/2009-11/msg00089.html
